\thispagestyle{plain}
\begin{center}
    \Large \textbf{\uppercase{Abstract}}
\end{center}
\vspace{3\baselineskip}
\noindent
%----------------------------------------------------------
Food waste and hunger are two major global challenges that exist simultaneously in many societies. Restaurants, households and event organizers discard large amounts of edible food every day, while many people still lack access to sufficient food. One of the key reasons for this imbalance is the lack of an efficient system that connects food donors with organizations that distribute food to those in need. This project presents a Food Donation Management System, a web-based platform designed to reduce food waste and improve food redistribution.

The system provides a centralized digital platform where donors can register and list surplus food items, while NGOs can browse available donations and request them for distribution. An administrative panel is included to monitor requests, approve or reject them, and maintain system transparency. The platform is developed using web technologies that include PHP, MySQL, HTML, and CSS, ensuring a simple and accessible interface for users.

By improving coordination between donors and charitable organizations, the system helps ensure that surplus food reaches people in need before it becomes waste. The project also contributes to global sustainability efforts, particularly Zero Hunger (SDG-2) and Responsible Consumption and Production (SDG-12). In general, the system demonstrates how technology can be used to address social problems and promote more efficient food distribution.


%----------------------------------------------------------
\vspace{\baselineskip}
\noindent
%----------------------------------------------------------

%----------------------------------------------------------
